---
title: "Mean Comparisons with backcalc"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Mean Comparisons with backcalc}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(comment = NA)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

## Mean Comparisons with `backcalc`

This vignette demonstrates a full mean comparison workflow using `backcalc` to derive summary statistics and DEVISE to format and plot the results. The steps progress from computing condition intervals to a final comparison.

```{r toc, echo=FALSE}
knitr::current_input() -> thisfile
revised_toc(thisfile, base_level = 3, toc_depth = 4)
```

---

### Load the Packages

```{r, include=FALSE}
if (!require(remotes)) install.packages("remotes")

if (!require(backcalc)) {remotes::install_github("cwendorf/backcalc")}
library(backcalc)

if (!require(DEVISE)) {remotes::install_github("cwendorf/DEVISE")}
library(DEVISE)
```

### Examine the Conditions (Summary Statistics Input)

#### Obtain the Statistics

Use backcalc to compute confidence intervals for each condition from summary statistics.

```{r}
backcalc_means(m = 8.000, sd = 1.414, n = 10) -> Level1
backcalc_means(m = 11.000, sd = 2.211, n = 10) -> Level2
backcalc_means(m = 12.000, sd = 2.162, n = 10) -> Level3

rbind(Level1, Level2, Level3) |> extract_intervals() -> Conditions
c("Level1", "Level2", "Level3") -> rownames(Conditions)
```

#### Display the Conditions

Format and visualize the condition intervals.

```{r}
Conditions |> style_matrix(title = "Table 1: Means and Confidence Intervals", style = "apa")
Conditions |> plot_conditions(title = "Figure 1: Conditions Confidence Intervals", values = TRUE)
```

### Make a Comparison (Summary Statistics Input)

#### Obtain the Statistics

Compute the comparison interval between the two selected conditions.

```{r}
backcalc_means(m = c(11.000, 8.000), sd = c(2.211, 1.414), n = c(10, 10)) |> extract_intervals() -> Difference

rbind(Level1, Level2, Difference) -> Comparison
c("Level1", "Level2", "Difference") -> rownames(Comparison)
```

#### Display the Comparison

Present the comparison in a formatted table and plot.

```{r}
Comparison |> style_matrix(title = "Table 2: Means, Confidence Intervals, and Comparison", style = "apa")
Comparison |> plot_comparison(title = "Figure 2: Comparison Confidence Intervals", values = TRUE)
```
