---
title: "Direct Input Examples"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Direct Input Examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(comment = NA)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(remotes)) install.packages("remotes")
if (!require(DEVISE)) {remotes::install_github("cwendorf/DEVISE")}
library(DEVISE)
```

## Direct Input Examples

Tjhis vignette demonstrates how to directly input reported statistics from published or secondary sources to present estimation results. `DEVISE` handles the assembly, formatting, and visualization of these externally-sourced values without any computation. 

```{r toc, echo=FALSE}
knitr::current_input() |> revised_toc(base_level = 3, toc_depth = 4)
```

---

### Case 1: Estimates from a Single Source

#### Examine the Conditions

When working with published studies or secondary data sources, you can directly input the reported estimates and confidence intervals. This approach is useful for meta-analyses, literature reviews, or when reconstructing results from research reports.

```{r}
c(Estimate = 8.000, LL = 6.988, UL = 9.012) -> Level1
c(Estimate = 11.000, LL = 9.418, UL = 12.582) -> Level2
c(Estimate = 12.000, LL = 10.248, UL = 13.752) -> Level3

rbind(Level1, Level2, Level3) -> Conditions
c("Level1", "Level2", "Level3") -> rownames(Conditions)
```

#### Display the Conditions

Format the condition matrix and visualize the intervals.

```{r,direct-conditions}
Conditions |> style_matrix(title = "Table 1: Means and Confidence Intervals for Conditions", style = "apa")
Conditions |> plot_conditions(title = "Figure 1: Means and Confidence Intervals for Conditions", values = TRUE)
```

#### Examine a Comparison

In addition to condition-level estimates, you can directly input comparison results reported in published studies.

```{r}
c(Estimate = 3.000, LL = 1.234, UL = 4.766) -> Difference

rbind(Level1, Level2, Difference) -> Comparison
c("Level1", "Level2", "Difference") -> rownames(Comparison)
```

#### Display a Comparison

Present the comparison in a formatted table and plot.

```{r,direct-comparison}
Comparison |> style_matrix(title = "Table 2: Reported Means and Confidence Intervals for a Comparison", style = "apa")
Comparison |> plot_comparison(title = "Figure 2: Reported Means and Confidence Intervals for a Comparison", values = TRUE)
```

### Case 2: Estimates from Multiple Sources

#### Examine the Studies

When synthesizing results from multiple publications, DEVISE makes it easy to organize and present findings from different sources.

```{r}
c(Estimate = 11.000, LL = 9.418, UL = 12.582) -> Study1
c(Estimate = 10.800, LL = 9.234, UL = 12.366) -> Study2
c(Estimate = 11.200, LL = 9.654, UL = 12.746) -> Study3

rbind(Study1, Study2, Study3) -> MultiSource
c("Study 1", "Study 2", "Study 3") -> rownames(MultiSource)
```

#### Display the Studies

Format and visualize results from multiple sources for comparison.

```{r,direct-multi}
MultiSource |> style_matrix(title = "Table 3: Means and Confidence Intervals Across Studies", style = "apa")
MultiSource |> plot_conditions(title = "Figure 3: Means and Confidence Intervals Across Studies", values = TRUE)
```
