title: "Comparison Vignette with Direct Input"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Comparison Vignette with Direct Input}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(comment = NA)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(DEVISE)) {
  if (!require(remotes)) install.packages("remotes")
  remotes::install_github("cwendorf/DEVISE")
}
library(DEVISE)
```

## Comparison Vignette with Direct Input

```{r toc, echo=FALSE}
thisfile <- knitr::current_input()
revised_toc(thisfile, base_level = 3, toc_depth = 4)
```

---

### Input the Statistics for Each Condition

```{r}
c(Estimate = 8.000, LL = 6.988, UL = 9.012) -> Level1
c(Estimate = 11.000, LL = 9.418, UL = 12.582) -> Level2
c(Estimate = 12.000, LL = 10.248, UL = 13.752) -> Level3

rbind(Level1, Level2, Level3) -> Conditions
c("Level1", "Level2", "Level3") -> rownames(Conditions)
```

### Display the Conditions

```{r}
Conditions |> style_matrix(title = "Table 1: Means and Confidence Intervals", style = "apa")
Conditions |> plot_conditions(title = "Figure 1: Conditions Confidence Intervals", values = TRUE)
```

### Input the Comparison Statistics

```{r}
c(Estimate = 3.000, LL = 1.234, UL = 4.766) -> Difference

rbind(Level1, Level2, Difference) -> Comparison
c("Level1", "Level2", "Difference") -> rownames(Comparison)
```

### Display the Comparison

```{r}
Comparison |> style_matrix(title = "Table 2: Means, Confidence Intervals, and Comparison", style = "apa")
Comparison |> plot_comparison(title = "Figure 2: Comparison Confidence Intervals", values = TRUE)
```
