---
title: "Direct Input Cases"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Direct Input Cases}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(comment = NA)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

## Direct Input Cases

This vignette demonstrates how to directly input reported statistics from published or secondary sources to present estimation results. DEVISE handles the assembly, formatting, and visualization of these externally-sourced values without any computation.

```{r toc, echo=FALSE}
knitr::current_input() -> thisfile
revised_toc(thisfile, base_level = 3, toc_depth = 4)
```

---

### Load the Packages

```{r, include=FALSE}
if (!require(remotes)) install.packages("remotes")
if (!require(DEVISE)) {remotes::install_github("cwendorf/DEVISE")}
library(DEVISE)
```

### Input Condition Estimates from Published Sources

#### Enter the Reported Statistics

When working with published studies or secondary data sources, you can directly input the reported estimates and confidence intervals. This approach is useful for meta-analyses, literature reviews, or when reconstructing results from research reports.

```{r}
c(Estimate = 8.000, LL = 6.988, UL = 9.012) -> Level1
c(Estimate = 11.000, LL = 9.418, UL = 12.582) -> Level2
c(Estimate = 12.000, LL = 10.248, UL = 13.752) -> Level3

rbind(Level1, Level2, Level3) -> Conditions
c("Level1", "Level2", "Level3") -> rownames(Conditions)
```

#### Display the Conditions

Format the condition matrix for professional presentation.

```{r}
Conditions |> style_matrix(title = "Table 1: Reported Means and Confidence Intervals", style = "apa")
```

#### Visualize the Conditions

Create a plot of the condition confidence intervals.

```{r}
Conditions |> plot_conditions(title = "Figure 1: Reported Condition Estimates", values = TRUE)
```

### Input Comparison Results from Published Sources

#### Enter the Comparison

In addition to condition-level estimates, you can directly input comparison results reported in published studies.

```{r}
c(Estimate = 3.000, LL = 1.234, UL = 4.766) -> Difference

rbind(Level1, Level2, Difference) -> Comparison
c("Level1", "Level2", "Difference") -> rownames(Comparison)
```

#### Display the Comparison

Present the comparison results in a formatted table alongside the conditions.

```{r}
Comparison |> style_matrix(title = "Table 2: Reported Means, Confidence Intervals, and Comparison", style = "apa")
```

#### Visualize the Comparison

Create a comparison plot showing both condition estimates and their difference.

```{r}
Comparison |> plot_comparison(title = "Figure 2: Reported Comparison Results", values = TRUE)
```

### Multiple Comparisons from Different Sources

#### Combine Results Across Studies

When synthesizing results from multiple publications, DEVISE makes it easy to organize and present findings from different sources.

```{r}
c(Estimate = 11.000, LL = 9.418, UL = 12.582) -> Source1_Level2
c(Estimate = 10.800, LL = 9.234, UL = 12.366) -> Source2_Level2
c(Estimate = 11.200, LL = 9.654, UL = 12.746) -> Source3_Level2

rbind(Source1_Level2, Source2_Level2, Source3_Level2) -> MultiSource
c("Study 1", "Study 2", "Study 3") -> rownames(MultiSource)
```

#### Display Combined Results

Format and visualize results from multiple sources for comparison.

```{r}
MultiSource |> style_matrix(title = "Table 3: Level 2 Estimates Across Studies", style = "apa")
MultiSource |> plot_conditions(title = "Figure 3: Level 2 Estimates from Multiple Sources", values = TRUE)
```

