---
title: "Mean Comparisons with EASI"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Mean Comparisons with EASI}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(comment = NA)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

## Mean Comparisons with `EASI`

This vignette demonstrates two workflows with EASI: one using raw data and one using summary statistics. Each workflow follows the same pattern of building condition intervals, then generating a comparison.

```{r toc, echo=FALSE}
knitr::current_input() -> thisfile
revised_toc(thisfile, base_level = 3, toc_depth = 4)
```

---

### Load the Packages

```{r, include=FALSE}
if (!require(remotes)) install.packages("remotes")
if (!require(DEVISE)) {remotes::install_github("cwendorf/DEVISE")}
library(DEVISE)
if (!require(EASI)) {remotes::install_github("cwendorf/EASI")}
library(EASI)
```

### Case 1: Raw Data Input

#### Input the Data

Create a factor and outcome vector for the raw-data workflow.

```{r}
gl(3, 10, labels = c("Level1", "Level2", "Level3")) -> Factor
c(6, 8, 6, 8, 10, 8, 10, 9, 8, 7, 7, 13, 11, 10, 13, 8, 11, 14, 12, 11, 9, 16, 11, 12, 15, 13, 9, 14, 11, 10) -> Outcome
```

#### Examine the Conditions

Estimate condition means and intervals from the raw data.

```{r}
(Outcome~Factor) |> estimateMeans() -> Conditions
```

#### Display the Conditions

Format and visualize the condition intervals.

```{r}
Conditions |> style_matrix(title = "Table 1: Means and Confidence Intervals", style = "apa")
Conditions |> plot_conditions(title = "Figure 1: Conditions Confidence Intervals", values = TRUE)
```

### Make a Comparison

Subset to the two conditions that will be compared directly.

```{r}
Outcome[Factor %in% c("Level1", "Level2")] -> Outcome_Sub
Factor[Factor %in% c("Level1", "Level2")] -> Factor_Sub
```

#### Examine a Comparison

Estimate the comparison interval for the selected conditions.

```{r}
(Outcome_Sub~Factor_Sub) |> estimateComparison() -> Comparison
```

#### Display a Comparison

Present the comparison in a formatted table and plot.

```{r}
Comparison |> style_matrix(title = "Table 2: Means, Confidence Intervals, and Comparison", style = "apa")
Comparison |> plot_comparison(title = "Figure 2: Comparison Confidence Intervals", values = TRUE)
```

### Case 2: Summary Statistics Input

#### Input the Statistics

Provide summary statistics to demonstrate the summary-input workflow.

```{r}
c(N = 10, M = 8.000, SD = 1.414) -> Level1
c(N = 10, M = 11.000, SD = 2.211) -> Level2
c(N = 10, M = 12.000, SD = 2.449) -> Level3
construct(Level1, Level2, Level3, class = "bsm") -> IndependentSummary
```

#### Examine the Conditions

Estimate condition intervals from summary statistics.

```{r}
IndependentSummary |> estimateMeans() -> Conditions
```

#### Display the Conditions

Format and visualize the condition intervals.

```{r}
Conditions |> style_matrix(title = "Table 3: Means and Confidence Intervals", style = "apa")
Conditions |> plot_conditions(title = "Figure 3: Conditions Confidence Intervals", values = TRUE)
```

#### Examine a Comparison

Compute the comparison interval for the summary-input workflow.

```{r}
construct(Level1, Level2, class = "bsm") |> estimateComparison() -> Comparison
```

#### Display a Comparison

Present the comparison in a formatted table and plot.

```{r}
Comparison |> style_matrix(title = "Table 4: Means, Confidence Intervals, and Comparison", style = "apa")
Comparison |> plot_comparison(title = "Figure 4: Comparison Confidence Intervals", values = TRUE)
```
