---
title: "Reconstructed Information Examples"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Reconstructed Information Examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(comment = NA)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(remotes)) install.packages("remotes")
if (!require(DEVISE)) {remotes::install_github("cwendorf/DEVISE")}
library(DEVISE)
if (!require(backcalc)) {remotes::install_github("cwendorf/backcalc")}
library(backcalc)
```

## Reconstructed Information Examples

In conjunction with `DEVISE`, this vignette demonstrates how to use `backcalc` to reconstruct and compute confidence intervals for statistics beyond simple means. When published studies report summary statistics or test results, backcalc can reconstruct the full inferential statistics for various types of analyses.

```{r toc, echo=FALSE}
knitr::current_input() -> thisfile
revised_toc(thisfile, base_level = 3, toc_depth = 4)
```

---

### Case 1: Calculate Confidence Intervals

#### Examine the Conditions

Use backcalc to compute confidence intervals for each condition from summary statistics.

```{r}
backcalc_means(m = 8.000, sd = 1.414, n = 10) |> extract_intervals() -> Level1
backcalc_means(m = 11.000, sd = 2.211, n = 10) |> extract_intervals() -> Level2
backcalc_means(m = 12.000, sd = 2.162, n = 10) |> extract_intervals() -> Level3

rbind(Level1, Level2, Level3) -> Conditions
c("Level1", "Level2", "Level3") -> rownames(Conditions)
```

#### Display the Conditions

Format and visualize the condition intervals.

```{r,complete-conditions}
Conditions |> style_matrix(title = "Table 1: Means and Confidence Intervals for Conditions", style = "apa")
Conditions |> plot_conditions(title = "Figure 1: Means and Confidence Intervals for Conditions", values = TRUE)
```

#### Examine a Comparison

Compute the comparison interval between the two selected conditions.

```{r}
backcalc_means(m = c(11.000, 8.000), sd = c(2.211, 1.414), n = c(10, 10)) |> extract_intervals() -> Difference

rbind(Level1, Level2, Difference) -> Comparison
c("Level1", "Level2", "Difference") -> rownames(Comparison)
```

#### Display a Comparison

Present the comparison in a formatted table and plot.

```{r,complete-comparison}
Comparison |> style_matrix(title = "Table 2: Means and Confidence Intervals for a Comparison", style = "apa")
Comparison |> plot_comparison(title = "Figure 2: Means and Confidence Intervals for a Comparison", values = TRUE)
```

