---
title: "Basic Workflow"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Basic Workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 5, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE, comment = NA)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(remotes)) install.packages("remotes")
if (!require(DEVISE)) {remotes::install_github("cwendorf/DEVISE")}
library(DEVISE)
```

## Basic Workflow

`DEVISE` utilizes forward assignment (`->`) and pipe operators (`|>`) to keep examples readable and consistent. The overall goal is to read code left-to-right, from data creation to transformed output.

```{r toc, echo=FALSE}
knitr::current_input() |> revised_toc(base_level = 3, toc_depth = 1)
```

---

### Using Forward Assignment

To minimize visual backtracking, avoid left assignment (`<-`). Instead, use `->` to store objects after they are computed. This keeps the focus on the computation itself.

```{r}
data.frame(
  Group = rep(c("Group1", "Group2"), each = 5),
  Quiz = c(5, 6, 7, 5, 6, 8, 9, 7, 8, 9),
  Exam = c(8, 7, 9, 6, 7, 10, 9, 9, 8, 10)
) -> df

df
```

### Using Pipe Operators

To keep data flowing, pipe operators (`|>`) show step-by-step transformations. They help express a sequence of operations without temporary assignment.

```{r}
df |> subset(Group == "Group1")
df |> transform(Total = Quiz + Exam)
```

When several operations are needed, chain them in one pipeline so each step builds directly on the previous one. This keeps the workflow compact and readable from left to right.

```{r}
df |>
  subset(Group == "Group1") |>
  transform(Total = Quiz + Exam)
```

If the chained result will be reused later, capture it with forward assignment at the end.

```{r}
df |>
  subset(Group == "Group2") |>
  transform(Total = Quiz + Exam) -> group2_with_total

group2_with_total
```

### Extending the Workflow

`DEVISE` provides additional functions for data manipulation, result standardization, and visualization. They are designed to work seamlessly with forward assignment and pipe operators. For example:

```{r}
df |>
  compute_descriptives(Quiz ~ Group) |>
  name_rows(c("First Class", "Second Class")) |>
  style_matrix(title = "Table 1: Quiz Descriptives by Class", style = "apa")
```

For detailed information on all available functions, visit the Reference documentation.
