---
title: "Mean Comparisons with confintr"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Mean Comparisons with confintr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 5, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE, comment = NA)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(remotes)) install.packages("remotes")
if (!require(DEVISE)) {remotes::install_github("cwendorf/DEVISE")}
library(DEVISE)
if (!require(confintr)) {remotes::install_github("mayer79/confintr")}
library(confintr)
```

## Mean Comparisons with `confintr`

This vignette illustrates a mean comparison workflow using the confintr package to compute intervals and DEVISE to format and plot results. The steps move from condition intervals to the final comparison display.

```{r toc, echo=FALSE}
knitr::current_input() |> revised_toc(base_level = 3, toc_depth = 1)
```

---

### Case 1: Parametric Confidence Intervals

#### Input the Data

Create a dataset for confidence interval analysis.

```{r}
gl(3, 10, labels = c("Level1", "Level2", "Level3")) -> Factor
c(6, 8, 6, 8, 10, 8, 10, 9, 8, 7, 7, 13, 11, 10, 13, 8, 11, 14, 12, 11, 9, 16, 11, 12, 15, 13, 9, 14, 11, 10) -> Outcome
data.frame(Factor, Outcome) -> df
```

#### Examine the Conditions

Use `confintr` with the default parametric method for each condition.

```{r}
ci_mean(df$Outcome[df$Factor == "Level1"]) |> extract_intervals() -> Level1
ci_mean(df$Outcome[df$Factor == "Level2"]) |> extract_intervals() -> Level2
ci_mean(df$Outcome[df$Factor == "Level3"]) |> extract_intervals() -> Level3

rbind(Level1, Level2, Level3) -> Conditions
c("Level1", "Level2", "Level3") -> rownames(Conditions)
```

#### Display the Conditions

Format and visualize the parametric confidence intervals.

```{r,cr-case1-conditions}
Conditions |> style_matrix(title = "Table 1: Means and Parametric Confidence Intervals for Conditions", style = "apa")
Conditions |> plot_conditions(title = "Figure 1: Means and Parametric Confidence Intervals for Conditions", values = TRUE)
```

#### Examine a Comparison

Use the parametric method to compare conditions.

```{r}
ci_mean_diff(df$Outcome[df$Factor == "Level2"], 
             df$Outcome[df$Factor == "Level1"]) |> extract_intervals() -> Difference

rbind(Level1, Level2, Difference) -> Comparison
c("Level1", "Level2", "Difference") -> rownames(Comparison)
```

#### Display a Comparison

Present the parametric comparison results in tables and plots.

```{r,cr-case1-comparison}
Comparison |> style_matrix(title = "Table 2: Means and Parametric Confidence Intervals for a Comparison", style = "apa")
Comparison |> plot_comparison(title = "Figure 2: Means and Parametric Confidence Intervals for a Comparison", values = TRUE)
```

### Case 2: Bootstrap Confidence Intervals

#### Examine the Conditions

Use `confintr` with bootstrap methods for each condition.

```{r}
ci_mean(df$Outcome[df$Factor == "Level1"], type = "bootstrap", R = 10000) |> extract_intervals() -> Level1
ci_mean(df$Outcome[df$Factor == "Level2"], type = "bootstrap", R = 10000) |> extract_intervals() -> Level2
ci_mean(df$Outcome[df$Factor == "Level3"], type = "bootstrap", R = 10000) |> extract_intervals() -> Level3

rbind(Level1, Level2, Level3) -> Conditions
c("Level1", "Level2", "Level3") -> rownames(Conditions)
```

#### Display the Conditions

Format and visualize the bootstrap confidence intervals.

```{r,cr-case2-conditions}
Conditions |> style_matrix(title = "Table 3: Means and Bootstrap Confidence Intervals for Conditions", style = "apa")
Conditions |> plot_conditions(title = "Figure 3: Means and Bootstrap Confidence Intervals for Conditions", values = TRUE)
```

#### Examine a Comparison

Use the bootstrap method to compare conditions.

```{r}
ci_mean_diff(df$Outcome[df$Factor == "Level2"], 
             df$Outcome[df$Factor == "Level1"], 
             type = "bootstrap", 
             R = 10000) |> extract_intervals() -> Difference

rbind(Level1, Level2, Difference) -> Comparison
c("Level1", "Level2", "Difference") -> rownames(Comparison)
```

#### Display a Comparison

Present the bootstrap comparison results in tables and plots.

```{r,cr-case2-comparison}
Comparison |> style_matrix(title = "Table 4: Means and Bootstrap Confidence Intervals for a Comparison", style = "apa")
Comparison |> plot_comparison(title = "Figure 4: Means and Bootstrap Confidence Intervals for a Comparison", values = TRUE)
```
