---
title: "Data Helpers"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Data Helpers}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 5, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE, comment = NA)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(remotes)) install.packages("remotes")
if (!require(DEVISE)) {remotes::install_github("cwendorf/DEVISE")}
library(DEVISE)
```

## Data Helpers

This vignette demonstrates helper functions that operate on *raw data*, 
building datasets and preparing variables and formulas
for downstream analysis functions.

```{r toc, echo=FALSE}
knitr::current_input() |> revised_toc(base_level = 3, toc_depth = 1)
```

---

### Create Sample Data

`create_groups()` constructs a factor grouping variable by repeating labels
according to the requested group sizes.

```{r}
data.frame(
  Group = create_groups(k = 3, c(10, 10, 10), labels = c("Level1", "Level2", "Level3")),
  Outcome = c(6, 8, 6, 8, 10, 8, 10, 9, 8, 7, 7, 13, 11, 10, 13, 8, 11, 14, 12, 11, 9, 16, 11, 12, 15, 13, 9, 14, 11, 10),
  Quiz = c(5, 6, 7, 5, 6, 8, 9, 7, 8, 9, 6, 7, 8, 6, 7, 9, 10, 8, 9, 10, 7, 8, 9, 7, 8, 10, 11, 9, 10, 11),
  Exam = c(8, 7, 9, 6, 7, 10, 9, 9, 8, 10, 7, 8, 9, 7, 8, 10, 11, 9, 10, 11, 8, 9, 10, 8, 9, 11, 12, 10, 11, 12)
) -> df

df
```

### Evaluate Variables

`use_vars()` extracts one or more named columns from a data frame and passes
them to the next function. This avoids attaching the data frame or creating
temporary objects.

```{r}
# Single variable
df |> use_vars(Quiz)

# Multiple variables
df |> use_vars(Quiz, Exam)
```

`use_vars()` also accepts formula syntax, scoping the formula variables to
the data frame. This is useful for preparing inputs for model functions.

```{r}
# Formula captured from data columns
df |> use_vars(Quiz ~ Group)

# View the model frame from the captured formula
df |> use_vars(Quiz ~ Group) |> model.frame()
```

### Filter Formula Rows

`filter_rows()` restricts the data referenced by a formula to a subset of
groups and returns a formula with the filtered rows in its environment.
Use it when your downstream function expects a formula.

```{r}
# Pipe-friendly with filter_rows()
df |> use_vars(Outcome ~ Group) |> filter_rows(Group == c("Level1", "Level2")) |> model.frame()

# Use with a different subset and formula
df |> use_vars(Exam ~ Group + Quiz) |> filter_rows(Group == c("Level2", "Level3")) |> model.matrix()
```
