---
title: "Data Helpers"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Data Helpers}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 5, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE, comment = NA)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(remotes)) install.packages("remotes")
if (!require(DEVISE)) {remotes::install_github("cwendorf/DEVISE")}
library(DEVISE)
```

## Data Helpers

This vignette demonstrates data helper functions for selecting rows and columns, renaming, extracting vectors, and retaining intermediate results.

```{r toc, echo=FALSE}
knitr::current_input() |> revised_toc(base_level = 3, toc_depth = 4)
```

---

### Case 1: Create a Data Set

`create_groups()` constructs a grouping variable by repeating labels according to the requested group sizes. In this example, it's used in conjunction with building an entire data frame.

```{r}
data.frame(
  Group = create_groups(k = 3, c(10, 10, 10), labels = c("Level1", "Level2", "Level3")),
  Outcome = c(6, 8, 6, 8, 10, 8, 10, 9, 8, 7, 7, 13, 11, 10, 13, 8, 11, 14, 12, 11, 9, 16, 11, 12, 15, 13, 9, 14, 11, 10),
  Quiz = c(5, 6, 7, 5, 6, 8, 9, 7, 8, 9, 6, 7, 8, 6, 7, 9, 10, 8, 9, 10, 7, 8, 9, 7, 8, 10, 11, 9, 10, 11),
  Exam = c(8, 7, 9, 6, 7, 10, 9, 9, 8, 10, 7, 8, 9, 7, 8, 10, 11, 9, 10, 11, 8, 9, 10, 8, 9, 11, 12, 10, 11, 12)
) -> df

df |> head()
```

### Case 2: Select and Rename Data

Use extraction helpers to keep only the rows and columns needed for a specific task.

```{r}
df |> extract_columns(c("Group", "Outcome", "Quiz")) -> selected_cols
selected_cols |> head()

selected_cols |> extract_rows(c(1, 10, 20, 30)) -> selected_rows
selected_rows

selected_rows |> name_columns(c("Condition", "Response", "QuizScore")) -> renamed_cols
renamed_cols

renamed_cols |> name_rows(c("Case1", "Case10", "Case20", "Case30")) -> renamed_rows
renamed_rows
```

### Case 3: Extract Vectors from Results

`extract_vector()` can pull a single column (for reporting) or a single row (for follow-up calculations).

```{r}
df |> compute_descriptives(Outcome ~ Group) -> descriptives
descriptives

descriptives |> extract_vector("M") -> means
means

descriptives |> extract_vector("Level2") -> level2_stats
level2_stats
```

### Case 4: Use Objects in Pipelines

`use_vars()` helps evaluate variables and formulas inside pipelines.

```{r}
df |> use_vars(Quiz, Exam) |> cor()
```
