---
title: "Descriptive Statistics"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Descriptive Statistics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(comment = NA)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(remotes)) install.packages("remotes")
if (!require(DEVISE)) {remotes::install_github("cwendorf/DEVISE")}
library(DEVISE)
```

## Descriptive Statistics

This vignette demonstrates how to compute descriptive statistics using `DEVISE`. These functions help extract and summarize data for later analyses.

```{r toc, echo=FALSE}
knitr::current_input() |> revised_toc(base_level = 3, toc_depth = 1)
```

---

### Create Sample Data

Create a sample dataset with groups and multiple variables for demonstration purposes.

```{r}
data.frame(
  Group = rep(c("Group1", "Group2"), each = 5),
  Quiz = c(5, 6, 7, 5, 6, 8, 9, 7, 8, 9),
  Exam = c(8, 7, 9, 6, 7, 10, 9, 9, 8, 10)
) -> df
```

### Means and Standard Deviations

Compute descriptive statistics for the whole frame:

```{r}
df |> compute_descriptives()
```

Compute descriptive statistics for selected variables:

```{r}
df |> compute_descriptives(Quiz, Exam)
```

Compute descriptive statistics for a single variable grouped by another variable:

```{r}
df |> compute_descriptives(Quiz ~ Group)
```

Compute descriptive statistics for multiple variables grouped by another variable:

```{r}
df |> compute_descriptives(c(Quiz, Exam) ~ Group)
```

### Correlations and Covariances

Compute a correlation matrix for a whole frame:

```{r}
df |> compute_correlations()
```

Compute a correlation matrix for selected variables:

```{r}
df |> compute_correlations(Quiz, Exam)
```

Compute correlations separately for each group:

```{r}
df |> compute_correlations(c(Quiz, Exam) ~ Group)
```

Compute covariances instead of correlations:

```{r}
df |> compute_correlations(Quiz, Exam, type = "cov")
```
