---
title: "Calculating Descriptive Statistics"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Calculating Descriptive Statistics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(comment = NA)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(remotes)) install.packages("remotes")
if (!require(DEVISE)) {remotes::install_github("cwendorf/DEVISE")}
library(DEVISE)
```

## Calculating Descriptive Statistics

This vignette demonstrates how to compute and format descriptive statistics and correlations using `DEVISE`. These functions help extract, summarize, and visualize data characteristics for exploratory analysis and presentation.

```{r toc, echo=FALSE}
knitr::current_input() |> revised_toc(base_level = 3, toc_depth = 4)
```

---

### Case 1: Overall Descriptive Statistics

#### Create Sample Data

Create a sample dataset with groups and multiple variables for demonstration purposes.

```{r}
data.frame(
  Group = create_groups(k = 2, c(5, 5), labels = c("Group1", "Group2")),
  Quiz = c(5, 6, 7, 5, 6, 8, 9, 7, 8, 9),
  Exam = c(8, 7, 9, 6, 7, 10, 9, 9, 8, 10)
) -> df
```

#### Obtain Descriptive Statistics

Compute descriptive statistics without grouping:

```{r}
df |> compute_descriptives()
```

Format the results as an APA-style table:

```{r}
df |> compute_descriptives(Quiz, Exam) |> style_matrix(title = "Table 1: Descriptive Statistics", style = "apa")
```

### Case 2: Grouped Descriptive Statistics

#### Obtain Descriptive Statistics for a Single Variable

Compute descriptive statistics for a single variable grouped by another variable:

```{r}
df |> compute_descriptives(Quiz ~ Group)
```

Format with styling:

```{r}
df |> compute_descriptives(Quiz ~ Group) |> style_matrix(title = "Table 2: Descriptive Statistics by Group", style = "apa")
```

#### Obtain Descriptive Statistics for Multiple Variables

Compute descriptive statistics for multiple variables grouped by another variable:

```{r}
df |> compute_descriptives(c(Quiz, Exam) ~ Group)
```

### Case 3: Correlation Analysis

#### Compute Correlation Matrix

Compute a correlation matrix for multiple variables:

```{r}
df |> compute_correlations()
```

Format as a styled table:

```{r}
df |> compute_correlations(Quiz, Exam) |> style_matrix(title = "Table 3: Correlation Matrix", style = "apa")
```

#### Compute Correlation Matrices

Compute correlations separately for each group:

```{r}
df |> compute_correlations(c(Quiz, Exam) ~ Group)
```

#### Compute Covariance Matrix

Compute the covariance matrix instead of correlations:

```{r}
df |> compute_correlations(Quiz, Exam, type = "cov") |> style_matrix(title = "Table 4: Covariance Matrix", style = "apa")
```
