---
title: "Pipeline Helpers"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Pipeline Helpers}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 5, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE, comment = NA)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(remotes)) install.packages("remotes")
if (!require(DEVISE)) {remotes::install_github("cwendorf/DEVISE")}
library(DEVISE)
```

## Pipeline Helpers

Several `DEVISE` helpers are not specific to any analysis stage — they work equally well on raw data frames and on result matrices produced by analysis functions. These functions support a general pipe-and-assign style and can appear anywhere in a pipeline.

```{r toc, echo=FALSE}
knitr::current_input() |> revised_toc(base_level = 3, toc_depth = 1)
```

---

### Create Sample Data

Create a sample dataset with groups and multiple variables for demonstration purposes.

```{r, include=FALSE}
data.frame(
  Group = create_groups(k = 3, c(10, 10, 10), labels = c("Level1", "Level2", "Level3")),
  Outcome = c(6, 8, 6, 8, 10, 8, 10, 9, 8, 7, 7, 13, 11, 10, 13, 8, 11, 14, 12, 11, 9, 16, 11, 12, 15, 13, 9, 14, 11, 10),
  Quiz = c(5, 6, 7, 5, 6, 8, 9, 7, 8, 9, 6, 7, 8, 6, 7, 9, 10, 8, 9, 10, 7, 8, 9, 7, 8, 10, 11, 9, 10, 11)
) -> df
```

### Extracting Columns and Rows

`extract_columns()` keeps only the specified columns, accepting either
names or numeric indices. It preserves the object type — a data frame in,
a data frame out; a matrix in, a matrix out.

```{r}
# By name
df |> extract_columns(c("Group", "Quiz"))

# By index
df |> extract_columns(c(1, 3))
```

`extract_rows()` keeps only the specified rows, accepting numeric indices
or row names. Like `extract_columns()`, it is type-preserving.

```{r}
# By numeric index
df |> extract_rows(c(1, 11, 21))

# By row name number
df |>
  extract_columns(c("Group", "Outcome")) |>
  extract_rows(c(1, 11, 21))
```

`extract_vector()` returns a single row or column as a named vector. This is
useful when you need one slice of a data frame or matrix inside a pipeline.

```{r}
# Extract a column vector
df |> extract_vector("Outcome")
```

### Relabeling Rows and Columns

`name_rows()` and `name_columns()` assign new labels in-place within a
pipeline. They work on any data frame or matrix and do not require a
temporary assignment between steps.

```{r}
# Rename columns on a data frame
df |>
  extract_columns(c("Group", "Outcome")) |>
  name_columns(c("Condition", "Response"))

# Rename rows and columns on df-derived subset
df |>
  extract_columns(c("Outcome", "Quiz")) |>
  extract_rows(c(1, 11, 21)) |>
  name_rows(c("RowA", "RowB", "RowC")) |>
  name_columns(c("Pre", "Post"))
```

### Capturing an Object Mid-Pipeline

`keep_as()` saves the current pipeline value under a name in the calling
environment and then passes the value through unchanged. Use it whenever
you need to retain an intermediate result without branching the pipeline
into a separate assignment statement.

```{r}
# Save the full data frame, then continue narrowing it
df |>
  keep_as(full_df) |>
  extract_columns(c("Group", "Outcome")) |>
  keep_as(narrow_df)

nrow(full_df)
nrow(narrow_df)
```
