---
title: "Mean Comparisons with statpsych and spTools"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Mean Comparisons with statpsych and spTools}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 5, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE, comment = NA)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(remotes)) install.packages("remotes")
if (!require(DEVISE)) {remotes::install_github("cwendorf/DEVISE")}
library(DEVISE)
if (!require(statpsych)) {remotes::install_github("dgbonett/statpsych")}
library(statpsych)
if (!require(spTools)) {remotes::install_github("cwendorf/spTools")}
library(spTools)
```

## Mean Comparisons with `statpsych` and `spTools`

This vignette demonstrates two approaches: `statpsych` functions alone, and a combined `statpsych` + `spTools` workflow. Each approach computes condition intervals and then a direct comparison.

```{r toc, echo=FALSE}
knitr::current_input() |> revised_toc(base_level = 3, toc_depth = 1)
```

---

### Case 1: Summary Statistics Input

#### Examine the Conditions

Compute condition intervals using `statpsych` functions.

```{r}
ci.mean(alpha = .05, m = 8.000, sd = 1.414, n = 10) |> extract_intervals() -> Level1
ci.mean(alpha = .05, m = 11.000, sd = 2.211, n = 10) |> extract_intervals() -> Level2
ci.mean(alpha = .05, m = 12.000, sd = 2.449, n = 10) |> extract_intervals() -> Level3

rbind(Level1, Level2, Level3) -> Conditions
c("Level1", "Level2", "Level3") -> rownames(Conditions)
```

#### Display the Conditions

Format and visualize the condition intervals.

```{r,sp-case1-conditions}
Conditions |> style_matrix(title = "Table 1: Means and Confidence Intervals for Conditions", style = "apa")
Conditions |> plot_conditions(title = "Figure 1: Means and Confidence Intervals for Conditions", values = TRUE)
```

#### Examine a Comparison

Compute the comparison interval between two conditions.

```{r}
ci.mean2(alpha = .05, 11.000, 8.000, 2.211, 1.414, 10, 10) |> extract_intervals() |> extract_rows(1) -> Difference

rbind(Level1, Level2, Difference) -> Comparison
c("Level1", "Level2", "Difference") -> rownames(Comparison)
```

#### Display a Comparison

Present the comparison in a formatted table and plot.

```{r,sp-case1-comparison}
Comparison |> style_matrix(title = "Table 2: Means and Confidence Intervals for a Comparison", style = "apa")
Comparison |> plot_comparison(title = "Figure 2: Means and Confidence Intervals for a Comparison", values = TRUE)
```

### Case 2: Summary Statistics Input with `spTools`

#### Examine the Conditions

Compute condition intervals using vectorized functions from `statpsych` and `spTools`.

```{r}
ci.mean.vec(alpha = .05, m = c(8.000, 11.000, 12.000), sd = c(1.414, 2.211, 2.449), n = c(10, 10, 10)) |> extract_intervals() -> Conditions
c("Level1", "Level2", "Level3") -> rownames(Conditions)
```

#### Display the Conditions

Format and visualize the condition intervals.

```{r,sp-case2-conditions}
Conditions |> style_matrix(title = "Table 3: Means and Confidence Intervals for Conditions", style = "apa")
Conditions |> plot_conditions(title = "Figure 3: Means and Confidence Intervals for Conditions", values = TRUE)
```

#### Examine a Comparison

Compute the comparison interval between two conditions.

```{r}
ci.mean2.vec(alpha = .05, m = c(11.000, 8.000), sd = c(2.211, 1.414), n = c(10, 10)) |> extract_intervals() |> extract_rows(1) -> Difference

rbind(Conditions[1,], Conditions[2,], Difference) -> Comparison
c("Level1", "Level2", "Difference") -> rownames(Comparison)
```

#### Display a Comparison

Present the comparison in a formatted table and plot.

```{r,sp-case2-comparison}
Comparison |> style_matrix(title = "Table 4: Means and Confidence Intervals for a Comparison", style = "apa")
Comparison |> plot_comparison(title = "Figure 4: Means and Confidence Intervals for a Comparison", values = TRUE)
```
