---
title: "Median Comparisons with statpsych"
output:
  github_document:
    preserve_yaml: FALSE
vignette: >
  %\VignetteIndexEntry{Median Comparisons with statpsych}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 5, fig.path = "figures/", echo = TRUE, warning = FALSE, message = FALSE, comment = NA)
devtools::source_gist("8e6e5dc401e3fc1042ef7a030f9d19c7", filename = "revised_toc.R")
```

```{r, include=FALSE}
if (!require(remotes)) install.packages("remotes")
if (!require(DEVISE)) {remotes::install_github("cwendorf/DEVISE")}
library(DEVISE)
if (!require(statpsych)) {remotes::install_github("dgbonett/statpsych")}
library(statpsych)
```

## Median Comparisons with `statpsych`

This vignette demonstrates median confidence-interval workflows using `statpsych`, with parallel examples for between-subjects and within-subjects designs.

```{r toc, echo=FALSE}
knitr::current_input() |> revised_toc(base_level = 3, toc_depth = 1)
```

---

### Calculate Confidence Intervals (Between-Subjects Data)

Enter the data.

```{r}
y1 <- c(5.4, 6.1, 6.8, 7.0, 7.2, 7.5, 7.7, 7.9, 8.1, 8.4)
y2 <- c(6.0, 7.2, 8.1, 8.7, 9.0, 9.2, 9.6, 9.9, 10.1, 10.4)
y3 <- c(7.1, 8.0, 9.2, 9.8, 10.0, 10.5, 10.9, 11.3, 11.9, 12.4)
```

Compute condition intervals directly from raw observations.

```{r}
ci.median(alpha = .05, y = y1) |> extract_intervals() -> Level1
ci.median(alpha = .05, y = y2) |> extract_intervals() -> Level2
ci.median(alpha = .05, y = y3) |> extract_intervals() -> Level3
rbind(Level1, Level2, Level3) |> name_rows(c("Level 1", "Level 2", "Level 3")) -> Conditions
```

Format and visualize the condition intervals.

```{r,sp-med-case1-conditions}
Conditions |> style_matrix(title = "Table 1a: Medians and Confidence Intervals for Conditions (Between-Subjects)")
Conditions |> plot_conditions(title = "Figure 1a: Medians and Confidence Intervals for Conditions (Between-Subjects)")
```

Compute the comparison interval between two conditions.

```{r}
ci.median2(alpha = .05, y1 = y3, y2 = y1) |> extract_intervals() -> Difference
rbind(Level1, Level3, Difference) |> name_rows(c("Level 1", "Level 3", "Comparison")) -> Comparison
```

Present the comparison in a formatted table and plot.

```{r,sp-med-case1-comparison}
Comparison |> style_matrix(title = "Table 1b: Medians and Confidence Intervals for a Comparison (Between-Subjects)")
Comparison |> plot_comparison(title = "Figure 1b: Medians and Confidence Intervals for a Comparison (Between-Subjects)")
```

### Calculate Confidence Intervals (Within-Subjects Data)

Using the same observed values, now assume the data represents repeated measurements from the same participants across levels.

Compute condition intervals from each level.

```{r}
ci.median(alpha = .05, y = y1) |> extract_intervals() -> Level1
ci.median(alpha = .05, y = y2) |> extract_intervals() -> Level2
ci.median(alpha = .05, y = y3) |> extract_intervals() -> Level3
rbind(Level1, Level2, Level3) |> name_rows(c("Level 1", "Level 2", "Level 3")) -> Conditions
```

Format and visualize the condition intervals.

```{r,sp-med-case2-conditions}
Conditions |> style_matrix(title = "Table 2a: Medians and Confidence Intervals for Conditions (Within-Subjects)")
Conditions |> plot_conditions(title = "Figure 2a: Medians and Confidence Intervals for Conditions (Within-Subjects)")
```

Compute the comparison interval between two levels using a paired-samples median difference.

```{r}
ci.median.ps(alpha = .05, y1 = y3, y2 = y1) |> extract_intervals() -> Difference
rbind(Level1, Level3, Difference) |> name_rows(c("Level 1", "Level 3", "Comparison")) -> Comparison
```

Present the comparison in a formatted table and plot.

```{r,sp-med-case2-comparison}
Comparison |> style_matrix(title = "Table 2b: Medians and Confidence Intervals for a Comparison (Within-Subjects)")
Comparison |> plot_comparison(title = "Figure 2b: Medians and Confidence Intervals for a Comparison (Within-Subjects)")
```
